Gains and losses in rheumatoid arthritis data from inferCNV

### 2024-02-23 infercnv/reports/gains_and_losses.Rmd
check for truncated bams in mappings before submitting to nextflow

p_dat <-
  events %>%
  dplyr::ungroup() %>%
  dplyr::add_count(events) %>%
  dplyr::mutate(prop = n / dplyr::n()) %>%
  dplyr::filter(events != 'WT') %>%
  dplyr::mutate(
    events = events %>% 
      gsub('chr', '', .) %>% 
      gsub('_gain', '+', .) %>%
      gsub('_loss', '+', .),
    events = forcats::fct_infreq(events),
    label1 = scales::label_comma()(n), 
    label = dplyr::case_when(
      n < 10 ~ label1,
      TRUE ~ paste0(label1, ' (', round(prop*100, 2), '%)')
    ))
p_dat %>%
  ggplot(aes(x = events, fill = cell_group, label = label)) +
  geom_bar() +
  geom_text(aes(y = n), hjust = 0, vjust = -0.1, angle = 45, size = 2) +
  scale_x_discrete(guide = guide_axis(angle = -90)) +
  ylim(c(0, max(p_dat$n) * 1.1)) +
  theme_classic()
p_dat %>%
  ggplot(aes(x = forcats::fct_infreq(gains), fill = sample, label = label)) +
  geom_bar() +
  geom_text(aes(y = n), hjust = 0, vjust = -0.1, angle = 45, size = 2) +
  scale_x_discrete(guide = guide_axis(angle = -90)) +
  ylim(c(0, max(p_dat$n) * 1.1)) +
  theme_classic()
```

>>>>

p_dat <-
  events %>%
  dplyr::ungroup() %>%
  dplyr::add_count(events) %>%
  dplyr::mutate(prop = n / dplyr::n()) %>%
  dplyr::filter(events != 'WT') %>%
  dplyr::mutate(
    events = events %>% 
      gsub('chr', '', .) %>% 
      gsub('_gain', '+', .) %>%
      gsub('_loss', '+', .),
    events = forcats::fct_infreq(events),
    label1 = scales::label_comma()(n), 
    label = dplyr::case_when(
      n < 10 ~ label1,
      TRUE ~ paste0(label1, ' (', round(prop*100, 2), '%)')
    ))
p_dat %>%
  ggplot(aes(x = events, fill = cell_group, label = label)) +
  geom_bar() +
  geom_text(aes(y = n), hjust = 0, vjust = -0.1, angle = 45, size = 2) +
  scale_x_discrete(guide = guide_axis(angle = -90)) +
  ylim(c(0, max(p_dat$n) * 1.1)) +
  theme_classic()
p_dat %>%
  ggplot(aes(x = forcats::fct_infreq(events), fill = sample, label = label)) +
  geom_bar() +
  geom_text(aes(y = n), hjust = 0, vjust = -0.1, angle = 45, size = 2) +
  scale_x_discrete(guide = guide_axis(angle = -90)) +
  ylim(c(0, max(p_dat$n) * 1.1)) +
  theme_classic()
```
